### 2022-11-19 dissertation/chapters/08-results.tex
🚧 (results): Heuristic pools

Table~\ref{tab:results:standalone:metrics:loss} presents the empirical results for this experimental group, showing the average test loss and statistics for all the low-level heuristics, compared to the three variants of the \acs{BHH} that was implemented. The test loss is measured at the last epoch for each dataset, over all indepedent runs.

@@

This section provides the empirical results for the experimental group that compares the performance of different variants of the \acs{BHH} as it relates to the \index{heuristic pool}\textit{heuristic pool} hyper-parameter. Brief discussions follow and illustrations are provided for visual aid. This experimental group utilises the same three variants of the \acs{BHH} as was utilised in Section \ref{sec:results:standalone}, but provides an opportunity to look at the \acs{BHH} \index{heuristic pool}heuristic pool hyper-parameter in more depth.

Table \ref{tab:results:heuristic_pool:metrics} provides the ranked performance, per dataset, of each of the \acs{BHH} \index{heuristic pool}heuristic pool configurations. Similar to before, the performance rank is calculated as the average rank produced by each \index{heuristic pool}heuristic pool configuration, for all datasets, over all runs and all training epochs.

@@

@@

\begin{table}[htb]
	\centering
	\caption{Empirical results showing average rank and statistics for all heuristic pool configurations used by the \acs{BHH} across multiple datasets, for all independent runs and epochs.}
	\label{tab:results:heuristic_pool:metrics:loss}%
	\par\bigskip
	\resizebox{\textwidth}{!}{
		\begin{tabular}{r|lll}
			                             & \multicolumn{3}{c}{\textbf{Heuristic Pool - Average Loss}}                                                                                                                     \\
			\midrule
			\textbf{dataset}             & \multicolumn{1}{c}{\textbf{all}}                           & \multicolumn{1}{c}{\textbf{gd}}                         & \multicolumn{1}{c}{\textbf{mh}}                         \\
			\midrule
			\textbf{abalone}             & \cellcolor[rgb]{ 1,  .922,  .518}2.0587 ($\pm$0.088)       & \cellcolor[rgb]{ .388,  .745,  .482}2.0125 ($\pm$0.068) & \cellcolor[rgb]{ .973,  .412,  .42}2.2942 ($\pm$0.055)  \\
			\textbf{air quality}         & \cellcolor[rgb]{ .973,  .412,  .42}0.2729 ($\pm$0.016)     & \cellcolor[rgb]{ 1,  .922,  .518}0.2642 ($\pm$0.011)    & \cellcolor[rgb]{ .388,  .745,  .482}0.2637 ($\pm$0.007) \\
			\textbf{bank}                & \cellcolor[rgb]{ 1,  .922,  .518}0.2456 ($\pm$0.065)       & \cellcolor[rgb]{ .388,  .745,  .482}0.2164 ($\pm$0.005) & \cellcolor[rgb]{ .973,  .412,  .42}0.2562 ($\pm$0.011)  \\
			\textbf{bike}                & \cellcolor[rgb]{ 1,  .922,  .518}0.0651 ($\pm$0.02)        & \cellcolor[rgb]{ .388,  .745,  .482}0.0545 ($\pm$0.005) & \cellcolor[rgb]{ .973,  .412,  .42}0.1179 ($\pm$0.006)  \\
			\textbf{car}                 & \cellcolor[rgb]{ .388,  .745,  .482}0.1572 ($\pm$0.034)    & \cellcolor[rgb]{ 1,  .922,  .518}0.169 ($\pm$0.025)     & \cellcolor[rgb]{ .973,  .412,  .42}0.4891 ($\pm$0.077)  \\
			\textbf{diabetic}            & \cellcolor[rgb]{ .973,  .412,  .42}1.2983 ($\pm$0.66)      & \cellcolor[rgb]{ .388,  .745,  .482}0.8976 ($\pm$0.011) & \cellcolor[rgb]{ 1,  .922,  .518}0.9137 ($\pm$0.008)    \\
			\textbf{fish toxicity}       & \cellcolor[rgb]{ 1,  .922,  .518}0.1046 ($\pm$0.008)       & \cellcolor[rgb]{ .973,  .412,  .42}0.1056 ($\pm$0.008)  & \cellcolor[rgb]{ .388,  .745,  .482}0.1043 ($\pm$0.009) \\
			\textbf{forest fires}        & \cellcolor[rgb]{ .973,  .412,  .42}0.081 ($\pm$0.069)      & \cellcolor[rgb]{ .388,  .745,  .482}0.0586 ($\pm$0.034) & \cellcolor[rgb]{ 1,  .922,  .518}0.0621 ($\pm$0.038)    \\
			\textbf{housing}             & \cellcolor[rgb]{ .388,  .745,  .482}0.0941 ($\pm$0.017)    & \cellcolor[rgb]{ 1,  .922,  .518}0.0951 ($\pm$0.015)    & \cellcolor[rgb]{ .973,  .412,  .42}0.1169 ($\pm$0.019)  \\
			\textbf{iris}                & \cellcolor[rgb]{ 1,  .922,  .518}0.2411 ($\pm$0.295)       & \cellcolor[rgb]{ .973,  .412,  .42}0.3729 ($\pm$1.119)  & \cellcolor[rgb]{ .388,  .745,  .482}0.1809 ($\pm$0.164) \\
			\textbf{mushroom}            & \cellcolor[rgb]{ 1,  .922,  .518}0.0052 ($\pm$0.012)       & \cellcolor[rgb]{ .388,  .745,  .482}0.0009 ($\pm$0.001) & \cellcolor[rgb]{ .973,  .412,  .42}0.0774 ($\pm$0.02)   \\
			\textbf{parkinsons}          & \cellcolor[rgb]{ 1,  .922,  .518}0.0587 ($\pm$0.003)       & \cellcolor[rgb]{ .388,  .745,  .482}0.0587 ($\pm$0.003) & \cellcolor[rgb]{ .973,  .412,  .42}0.0658 ($\pm$0.003)  \\
			\textbf{student performance} & \cellcolor[rgb]{ 1,  .922,  .518}0.2359 ($\pm$0.102)       & \cellcolor[rgb]{ .973,  .412,  .42}0.2454 ($\pm$0.134)  & \cellcolor[rgb]{ .388,  .745,  .482}0.1947 ($\pm$0.014) \\
			\textbf{wine quality}        & \cellcolor[rgb]{ .388,  .745,  .482}1.0827 ($\pm$0.026)    & \cellcolor[rgb]{ 1,  .922,  .518}1.1028 ($\pm$0.039)    & \cellcolor[rgb]{ .973,  .412,  .42}1.1666 ($\pm$0.03)   \\
		\end{tabular}%

Similar to the outcomes provided in Section \ref{sec:results:standalone}, it is found that the bhh\_gd configuration yielded the best overall performance compared to the bhh\_all and bhh\_mh configurations. Figure~\ref{fig:results:heuristic_pool:descriptive:descriptive} provides a illustration of the descriptive plots for the different \acs{BHH} configurations as it relates to the performance of the different \index{heuristic pool}heuristic pool configurations, per dataset.

@@

Figure~\ref{fig:results:heuristic_pool:descriptive:cd} provides an illustration of the overall critical difference plots that illustrate the statistically significant differences in ranked performance for each \index{heuristic pool}heuristic pool configuration as it relates to all datasets, across all runs.

@@

From Figures~\ref{fig:results:heuristic_pool:descriptive:descriptive} and Figure~\ref{fig:results:heuristic_pool:descriptive:cd}, it is clear that the bhh\_gd configuration performs best overall, with statistically insignificant exceptions for the parkinsons and housing datasets.

From the results show in Section \ref{sec:results:standalone}, the gradient-based methods outperformed the \index{meta-heuristic}meta-heuristics in all cases. It then logically makes sense that the bhh\_gd configuration yields the best performance. However, the inclusion of \index{meta-heuristic}meta-heuristics is done as an attempt to provide a mechanism that could provide even better performance, as well as generalisation capabilities to other datasets. The benefits of a generalisation capability is not realised in this dissertation, since the gradient-based \index{heuristic}heuristics provided the best performance across datasets and overall. Furthermore, the gradient-based \index{heuristic}heuristics already produce good performance results, and improvement on those results are hard. Faster convergence is also difficult to achieve, since the \acs{BHH} needs sufficient time to explore the heuristic space. The benefit that the \acs{BHH} then brings is that it provides a mechanism where prior expert knowledge can be injected, before training starts. Since gradient-based \index{heuristic}heuristics perform well, future research can exploit this knowledge and provide a significant bias towards these gradient-based \index{heuristic}heuristics through the initialisation of the concentration parameters as is mentioned previously.

Similar to before, Figure~\ref{fig:results:heuristic_pool:figures:abalone} provides the train and test, loss and accuracy plot for an example classification dataset (abalone) as it relates to the heuristic pool experimental group. As before, the illustration is provided in log scale and illustrations of train and test loss and accuracy plots for other datasets are left out for brevity as they yield similar illustrations.

@@

Figure~\ref{fig:results:heuristic_pool:figures:forest_fires} provides the train and test loss plot for an example regression dataset (forest fires) as it relates to the heuristic pool experimental group. As before, the illustration is provided in log scale and illustration of train and test loss plots for other regression databases are left out for brevity.

@@

Figure~\ref{fig:results:population:descriptive:descriptive} provides a illustration of the descriptive plots for the different \acs{BHH} configurations as it relates to the performance of the different population size configurations, per dataset.

@@

Figure~\ref{fig:results:population:figures:student_performance} provides the train and test loss plot for an example regression dataset (student performance) as it relates to the population size experimental group. As before, the illustration is provided in log scale and illustration of train and test loss plots for other regression databases are left out for brevity.

@@

Figure~\ref{fig:results:credit:descriptive:descriptive} provides a illustration of the descriptive plots for the different \acs{BHH} configurations as it relates to the performance of the different credit assignment strategy configurations, per dataset.

@@

Figure~\ref{fig:results:credit:figures:housing} provides the train and test loss plot for an example regression dataset (housing) as it relates to the credit assignment strategy experimental group. As before, the illustration is provided in log scale and illustration of train and test loss plots for other regression databases are left out for brevity.

@@

Figure~\ref{fig:results:credit:descriptive:descriptive} provides a illustration of the descriptive plots for the different \acs{BHH} configurations as it relates to the performance of different reselection interval configurations, per dataset.

@@

Figure~\ref{fig:results:reselection:figures:bike} provides the train and test loss plot for an example regression dataset (bike) as it relates to the reselection interval experimental group. As before, the illustration is provided in log scale and illustration of train and test loss plots for other regression databases are left out for brevity.

@@

Figure~\ref{fig:results:replay:descriptive:descriptive} provides a illustration of the descriptive plots for the different \acs{BHH} configurations as it relates to the performance of different replay window size configurations, per dataset.

@@

Figure~\ref{fig:results:replay:figures:fish_toxicity} provides the train and test loss plot for an example regression dataset (fish toxicity) as it relates to the replay window size experimental group. As before, the illustration is provided in log scale and illustration of train and test loss plots for other regression databases are left out for brevity.

@@

Figure~\ref{fig:results:reanalysis:descriptive:descriptive} provides a illustration of the descriptive plots for the different \acs{BHH} configurations as it relates to the performance of different reanalysis interval configurations, per dataset.

@@

Figure~\ref{fig:results:reanalysis:figures:parkinsons} provides the train and test loss plot for an example regression dataset (parkinsons) as it relates to the renalysis interval experimental group. As before, the illustration is provided in log scale and illustration of train and test loss plots for other regression databases are left out for brevity.

@@

Figure~\ref{fig:results:burn_in:descriptive:descriptive} provides a illustration of the descriptive plots for the different \acs{BHH} configurations as it relates to the burn in window size configurations, per dataset.

@@

Figure~\ref{fig:results:burn_in:figures:parkinsons} provides the train and test loss plot for an example regression dataset (parkinsons) as it relates to the burn in window size experimental group. As before, the illustration is provided in log scale and illustration of train and test loss plots for other regression databases are left out for brevity.

@@

Figure~\ref{fig:results:normalise:descriptive:descriptive} provides a illustration of the descriptive plots for the \acs{BHH} configurations with the normalisation hyper-parameter enabled and disabled, per dataset.

@@

Figure~\ref{fig:results:normalise:figures:bike} provides the train and test loss plot for an example regression dataset (bike) as it relates to the normalisation experimental group. As before, the illustration is provided in log scale and illustration of train and test loss plots for other regression databases are left out for brevity.

@@

Figure~\ref{fig:results:discounted_rewards:descriptive:descriptive} provides a illustration of the descriptive plots for the \acs{BHH} configurations with the discounted rewards hyper-parameter enabled and disabled, per dataset.

@@

Figure~\ref{fig:results:discounted_rewards:figures:housing} provides the train and test loss plot for an example regression dataset (housing) as it relates to the discounted rewards experimental group. As before, the illustration is provided in log scale and illustration of train and test loss plots for other regression databases are left out for brevity.

>>>>

Table~\ref{tab:results:standalone:metrics:loss} presents the empirical results for this experimental group, showing the average test loss and statistics for all the low-level heuristics, compared to the three variants of the \acs{BHH} that was implemented. The test loss is measured at the last epoch for each dataset, over all independent runs.

@@

This section provides the empirical results for the experimental group that compares the performance of different variants of the \acs{BHH} as it relates to the \index{heuristic pool}\textit{heuristic pool} hyper-parameter. Brief discussions follow and illustrations are provided for visual aid. This experimental group utilises the same three variants of the \acs{BHH} as was utilised in Section \ref{sec:results:standalone}, but provides an opportunity to look at the \acs{BHH} \index{heuristic pool}heuristic pool hyper-parameter in more depth. These variants are denoted as follows. The \acs{BHH} baseline configuration with a \index{heuristic pool}heuristic pool that contains all the low-level heuristics is denoted as \textit{all}, the \acs{BHH} configuration with a \index{heuristic pool}heuristic pool that contains only gradient-based \index{heuristic}heuristics is denoted as \textit{gd}, and finally, the \acs{BHH} configuration with a \index{heuristic pool}heuristics pool that contains only \index{meta-heuristic}meta-heuristics is denoted as \textit{mh}.

Table~\ref{tab:results:heuristic_pool:metrics:loss} presents the empirical results for this experimental group, showing the average test loss and statistics for all the heuristic pool variants of the \acs{BHH} that was implemented. The test loss is measured at the last epoch for each dataset, over all independent runs.

\begin{table}[htb]
	\centering
	\caption{Empirical results showing average test loss and statistics for all heuristic pool configurations used by the \acs{BHH} across multiple datasets, for all independent runs and is measured at the last epoch.}
	\label{tab:results:heuristic_pool:metrics:loss}%
	\par\bigskip
	\resizebox{0.8\textwidth}{!}{
		\begin{tabular}{r|lll}
			                             & \multicolumn{3}{c}{\textbf{Heuristic Pool - Average Loss}}                                                                                                                     \\
			\midrule
			\textbf{dataset}             & \multicolumn{1}{c}{\textbf{all}}                           & \multicolumn{1}{c}{\textbf{gd}}                         & \multicolumn{1}{c}{\textbf{mh}}                         \\
			\midrule
			\textbf{abalone}             & \cellcolor[rgb]{ 1,  .922,  .518}2.0587 ($\pm$0.088)       & \cellcolor[rgb]{ .388,  .745,  .482}2.0125 ($\pm$0.068) & \cellcolor[rgb]{ .973,  .412,  .42}2.2942 ($\pm$0.055)  \\
			\textbf{air quality}         & \cellcolor[rgb]{ .973,  .412,  .42}0.2729 ($\pm$0.016)     & \cellcolor[rgb]{ 1,  .922,  .518}0.2642 ($\pm$0.011)    & \cellcolor[rgb]{ .388,  .745,  .482}0.2637 ($\pm$0.007) \\
			\textbf{bank}                & \cellcolor[rgb]{ 1,  .922,  .518}0.2456 ($\pm$0.065)       & \cellcolor[rgb]{ .388,  .745,  .482}0.2164 ($\pm$0.005) & \cellcolor[rgb]{ .973,  .412,  .42}0.2562 ($\pm$0.011)  \\
			\textbf{bike}                & \cellcolor[rgb]{ 1,  .922,  .518}0.0651 ($\pm$0.02)        & \cellcolor[rgb]{ .388,  .745,  .482}0.0545 ($\pm$0.005) & \cellcolor[rgb]{ .973,  .412,  .42}0.1179 ($\pm$0.006)  \\
			\textbf{car}                 & \cellcolor[rgb]{ .388,  .745,  .482}0.1572 ($\pm$0.034)    & \cellcolor[rgb]{ 1,  .922,  .518}0.169 ($\pm$0.025)     & \cellcolor[rgb]{ .973,  .412,  .42}0.4891 ($\pm$0.077)  \\
			\textbf{diabetic}            & \cellcolor[rgb]{ .973,  .412,  .42}1.2983 ($\pm$0.66)      & \cellcolor[rgb]{ .388,  .745,  .482}0.8976 ($\pm$0.011) & \cellcolor[rgb]{ 1,  .922,  .518}0.9137 ($\pm$0.008)    \\
			\textbf{fish toxicity}       & \cellcolor[rgb]{ 1,  .922,  .518}0.1046 ($\pm$0.008)       & \cellcolor[rgb]{ .973,  .412,  .42}0.1056 ($\pm$0.008)  & \cellcolor[rgb]{ .388,  .745,  .482}0.1043 ($\pm$0.009) \\
			\textbf{forest fires}        & \cellcolor[rgb]{ .973,  .412,  .42}0.081 ($\pm$0.069)      & \cellcolor[rgb]{ .388,  .745,  .482}0.0586 ($\pm$0.034) & \cellcolor[rgb]{ 1,  .922,  .518}0.0621 ($\pm$0.038)    \\
			\textbf{housing}             & \cellcolor[rgb]{ .388,  .745,  .482}0.0941 ($\pm$0.017)    & \cellcolor[rgb]{ 1,  .922,  .518}0.0951 ($\pm$0.015)    & \cellcolor[rgb]{ .973,  .412,  .42}0.1169 ($\pm$0.019)  \\
			\textbf{iris}                & \cellcolor[rgb]{ 1,  .922,  .518}0.2411 ($\pm$0.295)       & \cellcolor[rgb]{ .973,  .412,  .42}0.3729 ($\pm$1.119)  & \cellcolor[rgb]{ .388,  .745,  .482}0.1809 ($\pm$0.164) \\
			\textbf{mushroom}            & \cellcolor[rgb]{ 1,  .922,  .518}0.0052 ($\pm$0.012)       & \cellcolor[rgb]{ .388,  .745,  .482}0.0009 ($\pm$0.001) & \cellcolor[rgb]{ .973,  .412,  .42}0.0774 ($\pm$0.02)   \\
			\textbf{parkinsons}          & \cellcolor[rgb]{ 1,  .922,  .518}0.0587 ($\pm$0.003)       & \cellcolor[rgb]{ .388,  .745,  .482}0.0587 ($\pm$0.003) & \cellcolor[rgb]{ .973,  .412,  .42}0.0658 ($\pm$0.003)  \\
			\textbf{student performance} & \cellcolor[rgb]{ 1,  .922,  .518}0.2359 ($\pm$0.102)       & \cellcolor[rgb]{ .973,  .412,  .42}0.2454 ($\pm$0.134)  & \cellcolor[rgb]{ .388,  .745,  .482}0.1947 ($\pm$0.014) \\
			\textbf{wine quality}        & \cellcolor[rgb]{ .388,  .745,  .482}1.0827 ($\pm$0.026)    & \cellcolor[rgb]{ 1,  .922,  .518}1.1028 ($\pm$0.039)    & \cellcolor[rgb]{ .973,  .412,  .42}1.1666 ($\pm$0.03)   \\
		\end{tabular}%

Similar to before, Table \ref{tab:results:heuristic_pool:metrics:rank} provides the ranked performance, per dataset, of each of the \acs{BHH} \index{heuristic pool}heuristic pool configurations. The performance rank is calculated as the average rank produced by each \index{heuristic pool}heuristic pool configuration, for all datasets, over all runs and all epochs.

@@

	\resizebox{0.8\textwidth}{!}{

@@

Similar to the outcomes provided in Section \ref{sec:results:standalone}, by ranked performance over all epochs, it is found that the \textit{gd} configuration yielded the best overall performance compared to the \textit{all} and \textit{mh} configurations. However, when considering the test loss measured at the last epoch, there is no clear difference in performance overall. This illustrates the reasoning behind the use of the rank metric over all epochs to evaluate the overall training process, as the test loss outcome differs at different epochs and early stopping of the training process was not used.

Figure~\ref{fig:results:heuristic_pool:descriptive:descriptive} provides an illustration of the descriptive plots for the different \acs{BHH} configurations as it relates to the performance of the different \index{heuristic pool}heuristic pool configurations, per dataset. From this illustration it can clearly be seen that, by ranked performance, the \textit{gd} configuration produced better results overall, considering the entire training process.

@@

Figure~\ref{fig:results:heuristic_pool:descriptive:cd} provides an illustration of the overall critical difference plots that illustrate the statistically significant differences in ranked performance for each \index{heuristic pool}heuristic pool configuration as it relates to all datasets, across all independent runs and epochs.

@@

From Figures~\ref{fig:results:heuristic_pool:descriptive:descriptive} and~\ref{fig:results:heuristic_pool:descriptive:cd}, it is clear that the \textit{gd} configuration configuration performs best overall, with exceptions to the parkinsons and housing datasets, where the \textit{all} and \textit{gd} configurations performed equally well with statistically insignificant differences in their outcomes.

From the results shown in this section and Section \ref{sec:results:standalone}, the gradient-based \index{heuristic}heuristics outperformed the \index{meta-heuristic}meta-heuristics in almost all cases. It can then logically be concluded that the \acs{BHH} baseline configuration with only gradient-based \index{heuristic}heuristics in the \index{heuristic pool}heuristic pool yields the best performance. The inclusion of \index{meta-heuristic}meta-heuristics is done as an attempt to provide a mechanism that could provide even better performance, as well as generalisation capabilities to other datasets. The benefits of using \index{meta-heuristic}meta-heuristics in the \index{heuristic pool}heuristic pool is not realised in this dissertation, since the gradient-based \index{heuristic}heuristics provided the best overall performance across  all datasets. Furthermore, the standalone gradient-based \index{heuristic}heuristics already produce good performance results, and improvement on those results are hard. Faster convergence is also difficult to achieve, since the \acs{BHH} needs sufficient time to explore the heuristic space. The benefit that the \acs{BHH} then brings is that it provides a mechanism whereby prior expert knowledge can be injected, before training starts. Since gradient-based \index{heuristic}heuristics perform well, future research can exploit this knowledge and provide a significant bias towards these gradient-based \index{heuristic}heuristics through the initialisation of the concentration parameters related to these \index{heuristic}heuristics as mentioned previously.

Similar to before, Figure~\ref{fig:results:heuristic_pool:figures:abalone} provides an illustration of the train and test, loss and accuracy plots for an example classification dataset (abalone) as it relates to the \index{heuristic pool}heuristic pool experimental group. As before, the illustration is provided in log scale and illustrations for the other classification datasets are left out for brevity as they yield similar illustrations.

@@

Figure~\ref{fig:results:heuristic_pool:figures:forest_fires} provides the train and test loss plot for an example regression dataset (forest fires) as it relates to the heuristic pool experimental group. As before, the illustration is provided in log scale and illustrations for the other regression datasets are left out for brevity.

@@

Figure~\ref{fig:results:population:descriptive:descriptive} provides an illustration of the descriptive plots for the different \acs{BHH} configurations as it relates to the performance of the different population size configurations, per dataset.

@@

Figure~\ref{fig:results:population:figures:student_performance} provides the train and test loss plot for an example regression dataset (student performance) as it relates to the population size experimental group. As before, the illustration is provided in log scale and illustration of train and test loss plots for other regression datasets are left out for brevity.

@@

Figure~\ref{fig:results:credit:descriptive:descriptive} provides an illustration of the descriptive plots for the different \acs{BHH} configurations as it relates to the performance of the different credit assignment strategy configurations, per dataset.

@@

Figure~\ref{fig:results:credit:figures:housing} provides the train and test loss plot for an example regression dataset (housing) as it relates to the credit assignment strategy experimental group. As before, the illustration is provided in log scale and illustration of train and test loss plots for other regression datasets are left out for brevity.

@@

Figure~\ref{fig:results:credit:descriptive:descriptive} provides an illustration of the descriptive plots for the different \acs{BHH} configurations as it relates to the performance of different reselection interval configurations, per dataset.

@@

Figure~\ref{fig:results:reselection:figures:bike} provides the train and test loss plot for an example regression dataset (bike) as it relates to the reselection interval experimental group. As before, the illustration is provided in log scale and illustration of train and test loss plots for other regression datasets are left out for brevity.

@@

Figure~\ref{fig:results:replay:descriptive:descriptive} provides an illustration of the descriptive plots for the different \acs{BHH} configurations as it relates to the performance of different replay window size configurations, per dataset.

@@

Figure~\ref{fig:results:replay:figures:fish_toxicity} provides the train and test loss plot for an example regression dataset (fish toxicity) as it relates to the replay window size experimental group. As before, the illustration is provided in log scale and illustration of train and test loss plots for other regression datasets are left out for brevity.

@@

Figure~\ref{fig:results:reanalysis:descriptive:descriptive} provides an illustration of the descriptive plots for the different \acs{BHH} configurations as it relates to the performance of different reanalysis interval configurations, per dataset.

@@

Figure~\ref{fig:results:reanalysis:figures:parkinsons} provides the train and test loss plot for an example regression dataset (parkinsons) as it relates to the renalysis interval experimental group. As before, the illustration is provided in log scale and illustration of train and test loss plots for other regression datasets are left out for brevity.

@@

Figure~\ref{fig:results:burn_in:descriptive:descriptive} provides an illustration of the descriptive plots for the different \acs{BHH} configurations as it relates to the burn in window size configurations, per dataset.

@@

Figure~\ref{fig:results:burn_in:figures:parkinsons} provides the train and test loss plot for an example regression dataset (parkinsons) as it relates to the burn in window size experimental group. As before, the illustration is provided in log scale and illustration of train and test loss plots for other regression datasets are left out for brevity.

@@

Figure~\ref{fig:results:normalise:descriptive:descriptive} provides an illustration of the descriptive plots for the \acs{BHH} configurations with the normalisation hyper-parameter enabled and disabled, per dataset.

@@

Figure~\ref{fig:results:normalise:figures:bike} provides the train and test loss plot for an example regression dataset (bike) as it relates to the normalisation experimental group. As before, the illustration is provided in log scale and illustration of train and test loss plots for other regression datasets are left out for brevity.

@@

Figure~\ref{fig:results:discounted_rewards:descriptive:descriptive} provides an illustration of the descriptive plots for the \acs{BHH} configurations with the discounted rewards hyper-parameter enabled and disabled, per dataset.

@@

Figure~\ref{fig:results:discounted_rewards:figures:housing} provides the train and test loss plot for an example regression dataset (housing) as it relates to the discounted rewards experimental group. As before, the illustration is provided in log scale and illustration of train and test loss plots for other regression datasets are left out for brevity.
